Strong coupling between scales in a multi-scalar model of urban dynamics

### 2024-10-08 Docs/Papers/Multiscale/paper/paper.tex
.

\title[Multi-scalar urban dynamics model]{Strong coupling between scales in a multi-scalar model of urban dynamics}

@@

\cite{lockerby2015asynchronous} physics multiscale simulations
+ multiscale traffic models (Nancy?)

@@

In disciplines that are neighbour to urban modelling, methods have been developed for multi-scale models. For example in spatial epidemiology, \cite{banos2015importance} combines agent-based modelling for local diffusion dynamics with differential equations at the population scale. The NetLogo software for agent-based modelling includes a specific extension for multi-scale modelling \cite{hjorth2020levelspace}. Multi-scale models have also been used for the simulation of crowd dynamics \cite{crociani2016multi}. The study of traffic is also made more accurate by coupling macroscopic and microscopic models \cite{boulet2020coupling}. The management of ecosystems  requires integrating across actors and scales \citep{belem2013organizational}. These non-exhaustive illustrations highlight how the integration of scales is a crucial feature and issue in the understanding of complex systems \citep{chavalarias2009french}.

In other disciplines such as physics or engineering, the methodology and application of multi-scale modelling is much more mature.
% TODO examples physics

% TODO emphasize more the research problem

@@

% rq positioning: not large model but simple whih can be understood (cf requiem for large scale models)

>>>>

\title[Multi-scalar model of urban dynamics]{Strong coupling between scales in a multi-scalar model of urban dynamics}

@@

% multiscale traffic models (Nancy?) -> ? - not found -> more lit joueiai2014multiscale ok

@@

In disciplines that are neighbour to urban modelling, methods have been developed for multi-scale models. For example in spatial epidemiology, \cite{banos2015importance} combines agent-based modelling for local diffusion dynamics with differential equations at the population scale. The NetLogo software for agent-based modelling includes a specific extension for multi-scale modelling \cite{hjorth2020levelspace}. Multi-scale models have also been used for the simulation of crowd dynamics \cite{crociani2016multi}. The study of traffic is also made more accurate by coupling macroscopic and microscopic models \citep{boulet2020coupling,joueiai2014multiscale}.
Urban climate \citep{rasheed2009multiscale}
The management of ecosystems requires integrating across actors and scales \citep{belem2013organizational}. These non-exhaustive illustrations highlight how the integration of scales is a crucial feature but difficult issue to adress for the understanding of urban and social complex systems \citep{chavalarias2009french}.

In other disciplines such as physics or engineering, the methodology and application of multi-scale modelling has been studied more extensively. \cite{lockerby2015asynchronous}
% TODO examples physics

% TODO emphasize more the research problem
% rq positioning: not large model but simple whih can be understood (cf requiem for large scale models)
% \citep{batty2014can}

@@
